Homework 8

### 2019-11-07 hw8/MSimonsHW8.tex
hw 8 problem 4
Cleaning up hw8 problem 4
hw 8 problem 5

>>>>

\item
Let $a$, $b \in I$ such that
\[a = 2a_0 + 2a_{1}x + ... + 2a_{n}x^n
\]
and
\[b = 2b_0 + 2_b{1}x + ... 2b_{n}x^n
\]
and $a_i$ and $b_i$ are integers for all
$i$.  We know that $I$ holds under subtraction because
\begin{align*}
a - b &= (2a_0 + 2a_{1}x + ... + 2a_{n}x^{n}) - (2b_0 + 2_b{1}x + ... 2b_{n}x^n) \\
&= (2a_0 - 2b_0) + (2a_{1} - 2b_{1})x + ... + (2a_{n} - 2b_{n})x^n \\
&= 2(a_0 - b_0) + 2(a_{1} - b_{1})x + ... + 2(a_{n} - b_{n})x^n \\
\end{align*}

Next let
\[
c = c_0 + c_{1}x + ... + c_{n}x^n
\]
be an element of $\mathbb{Z}[x]$.
We know that $I$ absorbs multiplication because
\begin{align*}
ca &= (c_0 + c_{1}x + ... + c_{n}x^{n})(2a_0 + 2a_{1}x + ...+ 2a_{n}x^{n}) \\
&= 2(c_0 + c_{1}x + ... + c_{n}x^{n})(a_0 + a_{1}x + ... + a_{n}x^{n}) \\
&= 2(c_{0}a_{0} + (c_{0}a_{1} + c_{1}a_{0})x + (c_{0}a_{2} + c_{1}a_{1} + c_{2}a_{0})x^{2}
+ ... + c_{n}a_{n}x^{n}) \\
&= 2c_{0}a_{0} + 2(c_{0}a_{1} + c_{1}a_{0})x + 2(c_{0}a_{2} + c_{1}a_{1} + c_{2}a_{0})x^{2}
+ ... + 2c_{n}a_{n}x^{n} \\
&\subseteq I
\end{align*}
and
\begin{align*}
ac &= (2a_0 + 2a_{1}x + ...+ 2a_{n}x^{n})(c_0 + c_{1}x + ... + c_{n}x^{n}) \\
&= 2(a_0 + a_{1}x + ... + a_{n}x^{n})(c_0 + c_{1}x + ... + c_{n}x^{n}) \\
&= 2(a_{0}c_{0} + (a_{0}c_{1} + a_{1}c_{0})x + (a_{0}c_{2} + a_{1}c_{1} + a_{2}c_{0})x^{2}
+ ... + a_{n}c_{n}x^{n}) \\
&= 2a_{0}c_{0} + 2(a_{0}c_{1} + a_{1}c_{0})x + 2(a_{0}c_{2} + a_{1}c_{1} + a_{2}c_{0})x^{2}
+ ... + 2a_{n}c_{n}x^{n} \\
&\subseteq I
\end{align*}

Therefore, $I$ is an ideal of $\mathbb{Z}[x]$.

\item I claim that $I = (x^2 - 7)$.  Let $g(x)$, $f(x)$ be elements of $I$ such
that $g(x) = f(x)q(x)+r(x)$ and the degree of $r(x)$ is less than the degree
of $f(x)$.  We know that $g(x)$ is generated by $f(x)$ because
\begin{align*}
g(7) &= f(7)q(7) + r(7) \\
0 &= 0*q(7) + r(7) \\
0 &= 0 + r(7) \\
0 &= r(7)
\end{align*}
Therefore $I$ is finitely generated.
